The evolution of gene expression in the term placenta of viviparous mammals

### 2016-04-07 manuscript/manuscript.Rnw
use sans math, black links, and fix noteref

%\documentclass[english,12pt]{article}
\documentclass[doublespacing]{bmcart_dla}
\usepackage{fontspec}
\setmainfont{FreeSans}
\setsansfont{FreeSans}
\setmonofont{FreeMono}
\setmathrm{FreeSans}
\setmathsf{FreeSans}
\setmathtt{FreeSans}
%\usepackage[letterpaper,left=1in,right=1in,top=1in,bottom=1in,headheight=14pt]{geometry}
\usepackage[letterpaper]{geometry}
\usepackage{url}
% \usepackage{fancyhdr}
\usepackage{graphicx}
% \usepackage[bf]{caption}
\usepackage{rotating}
\usepackage{wrapfig}
\usepackage{booktabs}
\usepackage{float}
\usepackage{multirow}
\usepackage{setspace}
\usepackage{wrapfig}
% \usepackage{txfonts}
%\usepackage[plain]{fancyref}
\usepackage{acronym}
\usepackage{array}
\usepackage{dcolumn}
\usepackage{adjustbox}
\usepackage{longtable}
\usepackage{pdflscape}
\usepackage{amsmath}
% \usepackage{sfmath}
\usepackage[backend=biber,natbib=true,hyperref=true,citestyle=numeric-comp,style=nature,autocite=inline]{biblatex}
\addbibresource{references.bib}
% \usepackage[noblocks,auth-sc]{authblk}
\usepackage[hyperfigures,bookmarks,colorlinks,linkcolor=blue,urlcolor=blue,citecolor=blue]{hyperref}
%\usepackage[hyperfigures,bookmarks,colorlinks,citecolor=black,filecolor=black,linkcolor=black,urlcolor=black]{hyperref}
% Floats at end for journals
\usepackage[nolists,figuresfirst,nomarkers,heads]{endfloat}
\renewcommand{\efloatseparator}{\mbox{}}
%\AtBeginFigures{\newpage \renewcommand{\efloatseparator}{\mbox{}}\section*{Figure Legends}}
%\AtBeginTables{\newpage \section*{Tables}\renewcommand{\efloatseparator}{\mbox{}}}
\usepackage[nomargin,inline,draft]{fixme}
\newcommand{\DLA}[1]{\textcolor{red}{\fxnote{DLA: #1}}}
\newcommand{\DEW}[1]{\textcolor{purple}{\fxnote{DEW: #1}}}
% \usepackage[x11names,svgnames]{xcolor}
% \usepackage{texshade}
% \usepackage{tikz}
\usepackage{nameref}
\usepackage{xspace}
% this package will stretch the font slightly if necessary.
\usepackage{microtype}
\usepackage{zref-xr,zref-user}
\zxrsetup{toltxlabel}
\zexternaldocument*{supplemental_material}
\usepackage[capitalize]{cleveref}
% \newenvironment{narrow}[2]{%
%   \begin{list}{}{%
%       \setlength{\topsep}{0pt}%
%       \setlength{\leftmargin}{#1}%
%       \setlength{\rightmargin}{#2}%
%       \setlength{\listparindent}{\parindent}%
%       \setlength{\itemindent}{\parindent}%
%       \setlength{\parsep}{\parskip}}%
%   \item[]}{\end{list}}
% \def\newblock{\hskip}
% \newenvironment{paperquote}{%
%   \begin{quote}%
%      \it
%   }%
%   {\end{quote}}
% \renewcommand{\textfraction}{0.15}
% \renewcommand{\topfraction}{0.85}
% \renewcommand{\bottomfraction}{0.65}
% \renewcommand{\floatpagefraction}{0.60}
%\renewcommand{\baselinestretch}{1.8}
% \newenvironment{enumerate*}%
%   {\begin{enumerate}%
%     \setlength{\itemsep}{0pt}%
%     \setlength{\parskip}{0pt}}%
%   {\end{enumerate}}
% \newenvironment{itemize*}%
%   {\begin{itemize}%
%     \setlength{\itemsep}{0pt}%
%     \setlength{\parskip}{0pt}}%
%   {\end{itemize}}
% \setcounter{tocdepth}{3}
% \oddsidemargin 0.0in 
% \textwidth 6in
% \raggedbottom
% \clubpenalty = 10000
% \widowpenalty = 10000
% set a large emergency stretch to avoid issues with overfull boxes
% \setlength{\emergencystretch}{20em}
% make the afill smaller
% \renewcommand\Affilfont{\itshape\small}
\renewcommand\cite[1]{\autocite{#1}}
% \pagestyle{fancy}

@@

\begin{frontmatter}
\begin{fmbox}
\dochead{Research}%
\title{The evolution of gene expression in the term placenta of viviparous mammals}%
%
\author[addressref={aff1},email={don@donarmstrong.com},noteref={n1}]{\inits{DL}\fnm{Don L} \snm{Armstrong}}
\author[addressref={aff2},email={1mmcgowen1@gmail.com},noteref={n1}]{\inits{MR}\fnm{Michael R.} \snm{McGowen}}
\author[addressref={aff1},email={aweckle@illinois.edu}]{\inits{AL}\fnm{Amy} \snm{Weckle}}
\author[addressref={aff3},email={jacaravas@gmail.com}]{\inits{J}\fnm{Jason} \snm{Caravas}}
\author[addressref={aff4},email={agnewd@dcpah.msu.edu}]{\inits{D}\fnm{Dalen} \snm{Agnew}}
\author[addressref={aff5},email={kbenirschke@ucsd.edu}]{\inits{K}\fnm{Kurt} \snm{Benirschke}}
\author[addressref={aff6},email={suerumbaugh@gmail.com}]{\inits{S}\fnm{Sue} \snm{Savage-Rumbaugh}}
\author[addressref={aff11},email={nevo@research.haifa.ac.il}]{\inits{E}\fnm{Eviatar} \snm{Nevo}}
\author[addressref={aff7,aff8},email={cjkim@med.wayne.edu}]{\inits{CJ}\fnm{Chong J} \snm{Kim}}
\author[addressref={aff9},email={gunter.wagner@yale.edu}]{\inits{GP}\fnm{Günter P.} \snm{Wagner}}
\author[addressref={aff7},email={prbchiefstaff@med.wayne.edu}]{\inits{R}\fnm{Roberto} \snm{Romero}}
\author[addressref={aff1,aff6,aff10},corref={aff1},email={wildmand@illinois.edu}]{\inits{DE}\fnm{Derek E.} \snm{Wildman}}
\address[id=aff1]{Institute for Genomic Biology, University of Illinois at Urbana-Champaign, Urbana, IL, USA}
\address[id=aff2]{School of Biological and Chemical Sciences, Queen Mary, University of London, London, UK}
\address[id=aff3]{Center for Molecular Medicine and Genetics, Wayne State University School of Medicine, Detroit, MI, USA}
\address[id=aff4]{Diagnostic Center for Population and Animal Health, College of Veterinary Medicine, Michigan State University, East Lansing, MI, USA}
\address[id=aff5]{Department of Pathology, University of California San Diego, La Jolla, CA, USA}
\address[id=aff6]{Great Ape Trust/Bonobo Hope Sanctuary, Des Moines, IA, USA}
\address[id=aff7]{Perinatology Research Branch, Eunice Kennedy Shriver National Institute of Child Health and Human Development (NICHD), National Institutes of Health (NIH), Detroit, MI, USA}
\address[id=aff8]{Department of Pathology, Wayne State University School of Medicine, Detroit, MI, USA}
\address[id=aff9]{Department of Ecology and Evolutionary Biology and Yale Systems Biology Institute, Yale University, New Haven, CT, USA}
\address[id=aff10]{Department of Molecular and Integrative Physiology, University of Illinois at Urbana-Champaign, Urbana, IL, USA}
\address[id=aff11]{The Institute of Evolution, University of Haifa, Haifa, Israel}

>>>>

%\documentclass[english,12pt]{article}
\documentclass[doublespacing]{bmcart_dla}
\usepackage{fontspec}
\setmainfont{FreeSans}
\setsansfont{FreeSans}
\setmonofont{FreeMono}
\setmathrm{FreeSans}
\setmathsf{FreeSans}
\setmathtt{FreeSans}
%\usepackage[letterpaper,left=1in,right=1in,top=1in,bottom=1in,headheight=14pt]{geometry}
\usepackage[letterpaper]{geometry}
\usepackage{url}
% \usepackage{fancyhdr}
\usepackage{graphicx}
% \usepackage[bf]{caption}
\usepackage{rotating}
\usepackage{wrapfig}
\usepackage{booktabs}
\usepackage{float}
\usepackage{multirow}
\usepackage{setspace}
\usepackage{wrapfig}
% \usepackage{txfonts}
%\usepackage[plain]{fancyref}
\usepackage{acronym}
\usepackage{array}
\usepackage{dcolumn}
\usepackage{adjustbox}
\usepackage{longtable}
\usepackage{pdflscape}
\usepackage{amsmath}
\usepackage{sansmath}
\usepackage[backend=biber,natbib=true,hyperref=true,citestyle=numeric-comp,style=nature,autocite=inline]{biblatex}
\addbibresource{references.bib}
% \usepackage[noblocks,auth-sc]{authblk}
\usepackage[hyperfigures,bookmarks,colorlinks,linkcolor=black,urlcolor=black,citecolor=blue]{hyperref}
%\usepackage[hyperfigures,bookmarks,colorlinks,citecolor=black,filecolor=black,linkcolor=black,urlcolor=black]{hyperref}
% Floats at end for journals
\usepackage[nolists,figuresfirst,nomarkers,heads]{endfloat}
\renewcommand{\efloatseparator}{\mbox{}}
%\AtBeginFigures{\newpage \renewcommand{\efloatseparator}{\mbox{}}\section*{Figure Legends}}
%\AtBeginTables{\newpage \section*{Tables}\renewcommand{\efloatseparator}{\mbox{}}}
\usepackage[nomargin,inline,draft]{fixme}
\newcommand{\DLA}[1]{\textcolor{red}{\fxnote{DLA: #1}}}
\newcommand{\DEW}[1]{\textcolor{purple}{\fxnote{DEW: #1}}}
% \usepackage[x11names,svgnames]{xcolor}
% \usepackage{texshade}
% \usepackage{tikz}
\usepackage{nameref}
\usepackage{xspace}
% this package will stretch the font slightly if necessary.
\usepackage{microtype}
\usepackage{zref-xr,zref-user}
\zxrsetup{toltxlabel}
\zexternaldocument*{supplemental_material}
\usepackage[capitalize]{cleveref}
% \newenvironment{narrow}[2]{%
%   \begin{list}{}{%
%       \setlength{\topsep}{0pt}%
%       \setlength{\leftmargin}{#1}%
%       \setlength{\rightmargin}{#2}%
%       \setlength{\listparindent}{\parindent}%
%       \setlength{\itemindent}{\parindent}%
%       \setlength{\parsep}{\parskip}}%
%   \item[]}{\end{list}}
% \def\newblock{\hskip}
% \newenvironment{paperquote}{%
%   \begin{quote}%
%      \it
%   }%
%   {\end{quote}}
% \renewcommand{\textfraction}{0.15}
% \renewcommand{\topfraction}{0.85}
% \renewcommand{\bottomfraction}{0.65}
% \renewcommand{\floatpagefraction}{0.60}
%\renewcommand{\baselinestretch}{1.8}
% \newenvironment{enumerate*}%
%   {\begin{enumerate}%
%     \setlength{\itemsep}{0pt}%
%     \setlength{\parskip}{0pt}}%
%   {\end{enumerate}}
% \newenvironment{itemize*}%
%   {\begin{itemize}%
%     \setlength{\itemsep}{0pt}%
%     \setlength{\parskip}{0pt}}%
%   {\end{itemize}}
% \setcounter{tocdepth}{3}
% \oddsidemargin 0.0in 
% \textwidth 6in
% \raggedbottom
% \clubpenalty = 10000
% \widowpenalty = 10000
% set a large emergency stretch to avoid issues with overfull boxes
% \setlength{\emergencystretch}{20em}
% make the afill smaller
% \renewcommand\Affilfont{\itshape\small}
\renewcommand\cite[1]{\autocite{#1}}
% \pagestyle{fancy}

@@

\begin{frontmatter}
\begin{fmbox}
\dochead{Research}%
\title{The evolution of gene expression in the term placenta of viviparous mammals}%
%
\author[addressref={aff1},noteref={n1},email={don@donarmstrong.com}]{\inits{DL}\fnm{Don L} \snm{Armstrong}}
\author[addressref={aff2},noteref={n1},email={1mmcgowen1@gmail.com}]{\inits{MR}\fnm{Michael R.} \snm{McGowen}}
\author[addressref={aff1},email={aweckle@illinois.edu}]{\inits{AL}\fnm{Amy} \snm{Weckle}}
\author[addressref={aff3},email={jacaravas@gmail.com}]{\inits{J}\fnm{Jason} \snm{Caravas}}
\author[addressref={aff4},email={agnewd@dcpah.msu.edu}]{\inits{D}\fnm{Dalen} \snm{Agnew}}
\author[addressref={aff5},email={kbenirschke@ucsd.edu}]{\inits{K}\fnm{Kurt} \snm{Benirschke}}
\author[addressref={aff6},email={suerumbaugh@gmail.com}]{\inits{S}\fnm{Sue} \snm{Savage-Rumbaugh}}
\author[addressref={aff11},email={nevo@research.haifa.ac.il}]{\inits{E}\fnm{Eviatar} \snm{Nevo}}
\author[addressref={aff7,aff8},email={cjkim@med.wayne.edu}]{\inits{CJ}\fnm{Chong J} \snm{Kim}}
\author[addressref={aff9},email={gunter.wagner@yale.edu}]{\inits{GP}\fnm{Günter P.} \snm{Wagner}}
\author[addressref={aff7},email={prbchiefstaff@med.wayne.edu}]{\inits{R}\fnm{Roberto} \snm{Romero}}
\author[addressref={aff1,aff6,aff10},corref={aff1},email={wildmand@illinois.edu}]{\inits{DE}\fnm{Derek E.} \snm{Wildman}}
\address[id=aff1]{Institute for Genomic Biology, University of Illinois at Urbana-Champaign, Urbana, IL, USA}
\address[id=aff2]{School of Biological and Chemical Sciences, Queen Mary, University of London, London, UK}
\address[id=aff3]{Center for Molecular Medicine and Genetics, Wayne State University School of Medicine, Detroit, MI, USA}
\address[id=aff4]{Diagnostic Center for Population and Animal Health, College of Veterinary Medicine, Michigan State University, East Lansing, MI, USA}
\address[id=aff5]{Department of Pathology, University of California San Diego, La Jolla, CA, USA}
\address[id=aff6]{Great Ape Trust/Bonobo Hope Sanctuary, Des Moines, IA, USA}
\address[id=aff7]{Perinatology Research Branch, Eunice Kennedy Shriver National Institute of Child Health and Human Development (NICHD), National Institutes of Health (NIH), Detroit, MI, USA}
\address[id=aff8]{Department of Pathology, Wayne State University School of Medicine, Detroit, MI, USA}
\address[id=aff9]{Department of Ecology and Evolutionary Biology and Yale Systems Biology Institute, Yale University, New Haven, CT, USA}
\address[id=aff10]{Department of Molecular and Integrative Physiology, University of Illinois at Urbana-Champaign, Urbana, IL, USA}
\address[id=aff11]{The Institute of Evolution, University of Haifa, Haifa, Israel}
